\normalfont \normalsize \huge Battle of Online and Offline Consumption: \\ Comparative Analysis of Amazon and Walmart Stocks

### 2017-06-16 Battle_of_Online_and_Offline_Consumption.tex
I'm modifying section 4

\begin{document}
\maketitle
\section{Introduction}
Online consumption is a relative new and prevailing concept raised in recent decade. Amazon is arguably one of the most successful online firms. As of this writing, its market cap is over \$460 billion, almost twice than the large and well-known offline retailer, Wal-Mart's, with market cap about \$240 billion.

@@

\section{Data Processing}
In our research report, we use Walmart as the representative of offline retail industry and Amazon as that of online retail industry. We focus on the daily log return of Walmart stock and Amazon stock from January 3th, 2010 to December 30th, 2016, with 1761 observations. All the data are pulled from Wind Terminal.

@@

\section{Model Establishment}
\subsection{Model Specification}
First of all, we determine the model to capture the log return fluctuation of Amazon stock. Figure \ref{cf_AMZN}.(a) shows the sample ACF of the log returns, which suggests that there is no significant serial correlations. Figure \ref{cf_AMZN}.(b), showing the sample PACF of the log returns, also confirms our conclusion of no serial correlation. Then, we plot the sample ACF of the squared log returns for Amazon stock in Figure \ref{cf_AMZN}.(c). Combing the three plots, it seems that the log returns are neither serially correlated nor dependent. Similar results can also be found for Walmart stock in Figure \ref{cf_WMT} that the log returns for Walmart stock are serially uncorrelated and independent.

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.7]{img/cf_AMZN}
\caption{ACF and PACF of Amazon Stock}
\label{cf_AMZN}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.7]{img/cf_WMT}
\caption{ACF and PACF of Walmart Stock}
\label{cf_WMT}
\end{figure}

\subsection{Mean Equation}
The observations above suggest that the daily log returns of Amazon stock follow an ARMA(0,0) model, in other words, a white noise series. This is in agreement with the result suggested by the sample ACF in Figure 2(c) that all sample ACFs are close to zero. Therefore, we propose a mean equation that is simply a constant plus innovations, $r_t = \mu + a_t$, where $r_t$  is the log return of an asset at time $t$, $\mu$ is the estimate we get using a volatility model. The squared series $a_t^2$ is then used to check for conditional heteroscedasticity (ARCH effects). We perform the usual Ljung–Box statistics Q(m) to the $\{a_t^2\}$ series. The null hypothesis is that the first m lags of ACF of the $a_t^2$ series are zero.

The Ljung–Box statistics of the $a_t^2$ series shows ARCH effects with Q(5) = 9.6519, the p value of which is close to zero.

\subsection{Volatility Equation}
Here we entertain an ARCH(1) model and a GARCH(1,1) model for the volatility and we specify the model as the following:
\[ r_t = \mu+a_t, a_t = \sigma_t \epsilon_t \]
\[ \text{ARCH(1): } \sigma_t^2 = \alpha_0+\alpha_1 a_{t-1}^2 \]
\[ \text{GARCH(1,1): } \sigma_t^2= \alpha_0+\alpha_1 a_{t-1}^2+\beta_1 \sigma_{t-1}^2 \]
in which $\epsilon_t$, here in our model, we assume as a Gaussian innovation that is independent and identically distributed as a Normal distribution with mean 0 and variance 1.

\section{Estimation}

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(1) and GARCH(1,1) models for AMZN Stock} 
  \label{} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(1)} & statistic & 4.7873 & 10.2395 & 12.8693 & 3.9721 & 4.7376 & 5.1054 \\
& p-value & 0.9049 & 0.8044 & 0.8829 & 0.9486 & 0.9941 & 0.9997 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 4.1734 & 10.2365 & 12.8473 & 3.0443 & 4.2163 & 4.7107 \\
& p.value & 0.9392 & 0.8046 & 0.8838 & 0.9804 & 0.9969 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for AMZN Stock} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
\hline \\[-1.8ex] 
 mu & 0.115$^{**}$ & 0.137$^{***}$ \\ 
  & (0.046) & (0.046) \\ 
  & & \\ 
 omega & 3.515$^{***}$ & 1.020$^{***}$ \\ 
  & (0.149) & (0.344) \\ 
  & & \\ 
 alpha1 & 0.168$^{***}$ & 0.129$^{***}$ \\ 
  & (0.036) & (0.032) \\ 
  & & \\ 
 beta1 &  & 0.637$^{***}$ \\ 
  &  & (0.098) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & 3724.855 & 3720.010 \\ 
Akaike Inf. Crit. & 4.234 & 4.229 \\ 
Bayesian Inf. Crit. & 4.243 & 4.242 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Based on the results of log likelihood, AIC, and BIC for ARCH(1) model and GARCH(1,1) model, GARCH(1,1) is slightly more appropriate.

Consequently, we obtain a GARCH(1,1) to model the volatility:
\[ \sigma_t^2 = 1.0199+0.1286 a_{t-1}^2+0.6373\sigma_{t-1}^2 \]

where the standard errors of the parameters are 0.3435, 0.0315, 0.0984, respectively.

In conclusion, we propose the following mean equation and conditional heteroskedasticity model for AMZN stock
\[ r_t = 0.1367+a_t, \sigma_t^2 = 1.0199+0.1286a_{t-1}^2+0.6373\sigma_{t-1}^2. \]

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(1) and GARCH(1,1) models for WMT Stock} 
  \label{} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(1)} & statistic & 9,0085 & 15.1256 & 20.0360 & 2.1312 & 2.4483 & 4.4991 \\
& p-value & 0.5313 & 0.4424 & 0.4557 & 0.9952 & 0.9999 & 0.9999 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 8.8064 & 14.4575 & 18.5378 & 1.6428 & 1.9398 & 4.0184 \\
& p.value & 0.5506 & 0.4912 & 0.5520 & 0.9984 & 0.9999 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for WMT Stock} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
 mu & 0.037 & 0.033 \\ 
  & (0.023) & (0.024) \\ 
  & & \\ 
 omega & 0.863$^{***}$ & 0.442$^{**}$ \\ 
  & (0.036) & (0.187) \\ 
  & & \\ 
 alpha1 & 0.192$^{***}$ & 0.140$^{***}$ \\ 
  & (0.034) & (0.040) \\ 
  & & \\ 
 beta1 &  & 0.445$^{**}$ \\ 
  &  & (0.207) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & 2506.755 & 2506.020 \\ 
Akaike Inf. Crit. & 2.850 & 2.851 \\ 
Bayesian Inf. Crit. & 2.860 & 2.863 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Consequently, we obtain a ARCH(1) to model the volatility:
\[ \sigma_t^2 = 0.1286+0.1920 a_{t-1}^2 \]

where the standard errors of the parameters are 0.0358, and 0.03389, respectively.

In conclusion, we propose the following mean equation and conditional heteroskedasticity model for AMZN stock
\[ r_t = 0.0372+a_t, \sigma_t^2 = 0.1286+0.1920a_{t-1}^2. \]

\section{Prediction}

\section{Conclusion}

\section{Appendix}

>>>>

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%   Introduction   %%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Online consumption is a relative new and prevailing concept raised in recent decade. Amazon is arguably one of the most successful online firms. As of this writing, its market cap is over \$460 billion, almost twice than the large and well-known offline retailer, Wal-Mart's, with market cap about \$240 billion.

@@

%%%%%%%%%%%%%%%%%%%%%%   Data Processing   %%%%%%%%%%%%%%%%%%%%%%%
\section{Data Processing}
In our research report, we use Walmart as the representative of offline retail industry and Amazon as that of online retail industry. We focus on the daily log return of Walmart stock and Amazon stock from January 3th, 2010 to December 30th, 2016, with 1761 observations. All the data are pulled from Wind Terminal.

@@

%%%%%%%%%%%%%%%%%%%%%  Model Establishment   %%%%%%%%%%%%%%%%%%%%%%
\section{Model Establishment}
\subsection{Model Specification}
First of all, we determine the model to capture the log return fluctuation of Amazon stock. Figure \ref{cf_AMZN}.(a) shows the sample ACF of the log returns, which suggests that there is no significant serial correlations and the series is stationary. Observing the squared log returns for Amazon stock in Figure \ref{cf_AMZN}.(c) we find that the log returns are not serially correlated but dependent, which indicates the ARCH effect in the return series. Similar results can also be found for Walmart stock in Figure \ref{cf_WMT} that there also exists an ARCH effect in Walmart's return series.

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.4]{img/cf_AMZN}
\caption{ACF and PACF of Amazon Stock}
\label{cf_AMZN}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.4]{img/cf_WMT}
\caption{ACF and PACF of Walmart Stock}
\label{cf_WMT}
\end{figure}

\subsection{Mean Equation}
According to the Figure \ref{cf_AMZN}.(b), the daily log returns of Amazon stock follow an ARMA(0,0) model because there is no cutoff in the PACF of log return. Therefore, we propose a mean equation that is simply a constant plus innovations, $r_t = \mu + a_t$, where $r_t$  is the log return of an asset at time $t$, $\mu$ is the estimate of mean log return.

The $a_t^2$ series is then used to check for conditional heteroscedasticity (ARCH effects). To consolidate the observation results in Figure \ref{cf_AMZN}.(c), we perform the Ljung–Box statistics Q(m) to the $\{a_t^2\}$ series. The null hypothesis is that the first m lags of ACF of the $a_t^2$ series are zero. The results of Ljung–Box test shows an ARCH effect exists in this log return series with Q(5) = 9.6519, the p-value of which is close to zero.

\subsection{Volatility Equation}
Based on the Figure \ref{cf_AMZN}.(d), there is a sudden cutoff at lag-1 squared $a_t^2$. Hence, we entertain an ARCH(1) model and a GARCH(1,1) model for the volatility and we specify the model as the following:
\[ r_t = \mu+a_t, a_t = \sigma_t \epsilon_t \]
\[ \text{ARCH(1): } \sigma_t^2 = \alpha_0+\alpha_1 a_{t-1}^2 \]
\[ \text{GARCH(1,1): } \sigma_t^2= \alpha_0+\alpha_1 a_{t-1}^2+\beta_1 \sigma_{t-1}^2 \]
in which $\epsilon_t$, we assume as a Gaussian innovation that is independent and identically distributed follows a Normal distribution with mean zero and variance one.

%%%%%%%%%%%%%%%%%%%   Comparison & Estimation   %%%%%%%%%%%%%%%%%%%%
\section{Model Comparison and Estimation}
To determine the more adequate model for Amazon stock, we perform the Ljung-Box test for the standardized residuals and the squared standardized residuals. However, there is no evident difference between ARCH(1) model and GARCH(1,1) model according to the test results in Table \ref{lb_AMZN}. Then we use log likelihhod and information criteria to compare models and derive the estimation results in Table \ref{est_AMZN}.

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(1) and GARCH(1,1) models for AMZN Stock} 
  \label{lb_AMZN} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(1)} & statistic & 4.7873 & 10.2395 & 12.8693 & 3.9721 & 4.7376 & 5.1054 \\
& p-value & 0.9049 & 0.8044 & 0.8829 & 0.9486 & 0.9941 & 0.9997 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 4.1734 & 10.2365 & 12.8473 & 3.0443 & 4.2163 & 4.7107 \\
& p.value & 0.9392 & 0.8046 & 0.8838 & 0.9804 & 0.9969 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for AMZN Stock} 
  \label{est_AMZN} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
\hline \\[-1.8ex] 
 mu & 0.115$^{**}$ & 0.137$^{***}$ \\ 
  & (0.046) & (0.046) \\ 
 omega & 3.515$^{***}$ & 1.020$^{***}$ \\ 
  & (0.149) & (0.344) \\ 
 alpha1 & 0.168$^{***}$ & 0.129$^{***}$ \\ 
  & (0.036) & (0.032) \\ 
 beta1 &  & 0.637$^{***}$ \\ 
  &  & (0.098) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & -3724.855 & -3720.010 \\ 
Akaike Inf. Crit. & 4.234 & 4.229 \\ 
Bayesian Inf. Crit. & 4.243 & 4.242 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Based on the results in Table \ref{est_AMZN}, GARCH(1,1) model is more appropriate because it has the largest value of Log Likelihood and the smallest value of AIC and BIC. And all estimated parameters are highly significant under 1\% significance level.

Consequently, we propose an ARMA(0,0)+GARCH(1,1) model to depict the log return series of Amazon stock:
\[ r_t = 0.137+a_t\]
\[ a_t = \sigma_t \epsilon_t, \epsilon_t \sim N(0,1) \]
\[ \sigma_t^2 = 1.02+0.129a_{t-1}^2+0.637\sigma_{t-1}^2 \]

@@

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(1) and GARCH(1,1) models for WMT Stock} 
  \label{lb_WMT} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(1)} & statistic & 9.0085 & 15.1256 & 20.0360 & 2.1312 & 2.4483 & 4.4991 \\
& p-value & 0.5313 & 0.4424 & 0.4557 & 0.9952 & 0.9999 & 0.9999 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 8.8064 & 14.4575 & 18.5378 & 1.6428 & 1.9398 & 4.0184 \\
& p.value & 0.5506 & 0.4912 & 0.5520 & 0.9984 & 0.9999 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for WMT Stock} 
  \label{est_WMT} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
 mu & 0.037 & 0.033 \\ 
  & (0.023) & (0.024) \\ 
 omega & 0.863$^{***}$ & 0.442$^{**}$ \\ 
  & (0.036) & (0.187) \\ 
 alpha1 & 0.192$^{***}$ & 0.140$^{***}$ \\ 
  & (0.034) & (0.040) \\ 
 beta1 &  & 0.445$^{**}$ \\ 
  &  & (0.207) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & 2506.755 & 2506.020 \\ 
Akaike Inf. Crit. & 2.850 & 2.851 \\ 
Bayesian Inf. Crit. & 2.860 & 2.863 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

%%%%%%%%%%%%%%%%%%%%%%   Prediction   %%%%%%%%%%%%%%%%%%%%%%%
\section{Prediction}

%%%%%%%%%%%%%%%%%%%%%%   Conclusion   %%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%   Appendix   %%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix}
